---
title: "Tenant-Service Record Keeping in Toronto: Low Ratings Are More Common in Smaller Apartment Buildings"
author: 
  - Kexin Liu
thanks: "Code and data are available at: [https://github.com/cocoUofT/Apartment_Evaluation.git](https://github.com/cocoUofT/Apartment_Evaluation.git)."
date: 27 September 2026
date-format: long
abstract: "Tenant service records track reported problems and managers’ responses, helping ensure accountability in rental housing. This paper uses Toronto’s apartment-building evaluations from 2023 to September 2026 to study tenant-service-log ratings, their patterns across different building sizes, how they change over time, and differences across wards relative to benchmarks based on building-size composition. We found that, among buildings with a meaningful rating at their latest evaluation, 13.8% of buildings with 10–19 units had incomplete or outdated tenant service logs, whereas only 1.0% of buildings with 100 or more units had incomplete logs. These differences show where further investigation of record-keeping practices may be useful, although the causes and whether tenants’ problems were resolved promptly remain unclear from the log scores alone."
format: pdf
number-sections: true
bibliography: references.bib
---

\newpage

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(tinytable)

apartment <- read_csv("../data/02-analysis_data/analysis_data.csv")
scorechange <- read_csv("../data/02-analysis_data/score_change_data.csv")
```

# Introduction

When tenants report problems such as leaks or broken locks, keeping a record of the request and the response helps track how the problem was handled. Under Toronto’s RentSafeTO program, building owners are required to track tenant service requests and keep records of requests and responses for 24 months [@toronto_service_requests]. These records support accountability by documenting how buildings handle tenant concerns.

This requirement raises a question: how consistently are tenant-service records maintained across apartment buildings? This paper examines whether low log ratings are more common in smaller buildings, whether buildings initially receiving low ratings score better at later evaluations, and whether ward differences remain after accounting for their mix of building sizes.

Toronto’s apartment-building evaluations provide a way to examine differences in tenant-service record keeping across buildings[@toronto_apartment_data]. The tenant-service request log rating shows whether a building’s log was complete and properly updated at the time of evaluation[@toronto_evaluation_criteria]. The main analysis uses each building’s latest available evaluation from 2023 through 24 September 2026, covering 3,587 buildings.

Low tenant-service-log ratings were more common among smaller buildings. Among buildings rated either 1 or 3 at their latest evaluation, 13.8% of those with 10–19 units received a rating of 1, indicating an incomplete or outdated log, compared with 1.0% of buildings with at least 100 units. In the follow-up sample, smaller buildings were also more likely to receive a rating of 1 again at their latest evaluation. These patterns suggest groups of buildings where further investigation into record-keeping practices may be useful. However, they do not show that building size causes poor record keeping or that smaller buildings provide worse service.

The remainder of this paper is organized as follows. @sec-data introduces the dataset and variables, then examines log ratings by building size, changes at follow-up, and ward differences relative to building-size benchmarks. @sec-discussion considers possible explanations for the findings, the study’s limitations, and directions for future research. The appendix provides additional summary statistics, follow-up counts and evaluation intervals, and a detailed explanation of the ward benchmark calculation.

# Data {#sec-data}

All data preparation and analysis were conducted in R [@citeR]. The `opendatatoronto` package was used to download the data [@opendatatoronto], `tidyverse` to prepare and summarize the records [@tidyverse], and `testthat` to check the structure and consistency of the analysis data [@testthat]. Figures were created using `ggplot2` [@ggplot2], with numerical labels formatted using `scales` [@scales]. Tables were produced using `tinytable` [@tinytable].

## Overview

This study uses the City of Toronto’s Apartment Building Evaluation dataset, available through Open Data Toronto [@toronto_apartment_data]. The dataset contains evaluation records collected under RentSafeTO, which applies to rental apartment buildings with three or more storeys and ten or more units [@toronto_registration]. The dataset provides information such as tenant-service-log ratings, building size, and ward. Another relevant dataset available through Open Data Toronto is the *Apartment Building Registration* dataset, which provides information about registered properties [@toronto_registration_data]. However, it lacks clear evaluation metrics or records of repeated evaluations. These are needed to compare record keeping across building sizes and assess whether log ratings improve over time. The *Apartment Building Evaluation* dataset therefore serves as the primary data source for this study.

The analysis uses the 2023–current resource downloaded on September 24, 2026. It contains 6,731 evaluation records for 3,587 buildings, covering June 5, 2023, to September 22, 2026. Each record represents one building evaluation, so buildings evaluated more than once appear in multiple rows. The cleaned data contain one latest evaluation per building across Toronto’s 25 wards for size and ward comparisons. A separate dataset pairs each building’s earliest and latest evaluations to examine changes in log ratings.

These records are produced through building evaluations conducted by City bylaw enforcement officers. For the tenant service request log, the officer assesses whether a process exists for recording requests and whether the log is complete and updated [@toronto_evaluation_criteria]. This assessment turns into a rating recorded alongside some other characteristics of the building. The rating therefore describes the condition of the log at the time of evaluation. However, it does not directly measure the quality of repairs or tenants’ satisfaction. 

The analysis discusses evaluated RentSafeTO buildings in the downloaded dataset, rather than all rental homes or renters in Toronto. Moreover, the reported percentages describe buildings, not the proportion of tenants affected by incomplete or outdated records.

## Variables of Interest

### Building Size

Building size is measured by the number of confirmed residential units recorded at each building’s latest evaluation. Unit counts are available for all 3,587 buildings in the main sample and range from 10 to 793.

```{r}
#| label: fig-sizehistogram
#| echo: false
#| eval: true
#| warning: false
#| fig-cap: Distribution of confirmed unit counts at the latest evaluation of 3,587 buildings
#| fig-pos: H

# Histogram of confirmed unit distribution
ggplot(apartment, aes(x = `CONFIRMED UNITS`)) +
  geom_histogram(binwidth = 60, boundary = 0, closed = "left", fill = "grey",
                 colour = "grey") +
  scale_x_continuous(breaks = seq(0, 840, by = 120)) +
  labs(x = "Confirmed Units Per Building", y = "Number of Buildings") +
  theme_minimal()
```

@fig-sizehistogram shows that the distribution of confirmed units is right-skewed, with many smaller buildings and relatively few much larger buildings. The median is 51 units, while the mean is 91.2 units, reflecting the influence of larger buildings. Summary statistics for confirmed units are provided in @tbl-confirmunits in the appendix.

For comparisons of tenant-service-log ratings, confirmed unit counts are grouped into four categories: 10–19, 20–49, 50–99, and 100 or more units. These categories are adapted from the size groups used in the Canada Mortgage and Housing Corporation’s Rental Market Report: Greater Toronto Area [@cmhc2018, p. 29]. The smallest category starts at 10 units, matching the standard in this analysis, while the report’s two largest categories are combined into a single group of 100 or more units here. The same four categories are used throughout the analysis. @tbl-sizegroup reports the number and percentage of buildings in each size category.

```{r}
#| label: tbl-sizegroup
#| tbl-cap: "Building counts and percentages by size category"
#| message: FALSE
#| echo: FALSE
#| tbl-pos: H

size_breaks <- c(9, 19, 49, 99, Inf)
size_labels <- c("10–19", "20–49", "50–99", "100+")

# Table: the four size groups
size_summary <- apartment |>
  mutate(size_group = cut(.data[["CONFIRMED UNITS"]], breaks = size_breaks, 
                          labels = size_labels)) |>
  filter(!is.na(size_group)) |>
  count(size_group, name = "Number of Buildings", .drop = FALSE) |>
  mutate(`Share (%)` = 100 * `Number of Buildings` / sum(`Number of Buildings`)) |>
  rename(`Building Size` = size_group)

tt(size_summary) |>
  format_tt(escape = TRUE) |>
  format_tt(j = 2, digits = 0, num_fmt = "decimal", num_mark_big = ",") |>
  format_tt(j = 3, digits = 1, num_fmt = "decimal") |>
  style_tt(j = 2:3, align = "r")
```

### Tenant Service Log Score

The tenant service log score describes whether a building’s record of tenant requests was complete and properly updated at the time of evaluation. Under the City’s published criteria, a score of 1 indicates an incomplete or outdated log, while a score of 3 indicates a complete log. A score of 2 is labelled “N/A” for this item [@toronto_evaluation_criteria]. The dataset also contains scores of 0, which are not defined in the published criteria and are reported separately as unspecified. These values are treated as categories rather than a continuous numerical scale.

@tbl-logscore shows the number and percentage of buildings receiving each score at their latest evaluation. Most buildings received a score of 3 (3,276 buildings, or 91.3%), while 208 buildings received a score of 1 (5.8%). The remaining 103 buildings received scores of 0 or 2.

```{r}
#| label: tbl-logscore
#| tbl-cap: "Building counts and percentages by tenant-log score"
#| message: FALSE
#| echo: FALSE
#| tbl-pos: H

# Table: the four scores
score_counts <- table(factor(apartment[["TENANT SERVICE REQUEST LOG"]],
                             levels = 0:3))
score_summary <- data.frame(Score = as.character(0:3),
                            `Published Meaning` = c("Not specified", 
                                                    "Not completed or properly 
                                                    updated",
                                                    "Not applicable", 
                                                    "Completed/full"),
                            Buildings = as.integer(score_counts),
                            `Share (%)` = 100 * as.integer(score_counts) 
                            / nrow(apartment),
                            check.names = FALSE)
tt(score_summary) |>
  format_tt(escape = TRUE) |>
  format_tt(j = 3, digits = 0, num_fmt = "decimal", num_mark_big = ",") |>
  format_tt(j = 4, digits = 1, num_fmt = "decimal") |>
  style_tt(j = c(3, 4), align = "r")
```

## Analysis

### Log Ratings by Building Size

The comparison includes the 3,484 buildings that received a tenant-service-log score of either 1 or 3 in their latest evaluation, excluding scores of 0 and 2. Within each size category, the percentage receiving a low rating is calculated as the number of buildings scoring 1 divided by the number scoring either 1 or 3.

@fig-sizescore shows that low ratings become less common as building size increases. Among buildings with 10–19 units, 13.8% received a score of 1. The proportion was 8.1% for buildings with 20–49 units and 3.1% for buildings with 50–99 units. Buildings with 100 or more units had the lowest percentage, at only 1.0%. This pattern indicates that incomplete or outdated tenant-service logs were more common among smaller buildings.

```{r}
#| label: fig-sizescore
#| echo: false
#| eval: true
#| warning: false
#| fig-cap: Percentage scoring 1, indicating incomplete or outdated logs, among 3,484 buildings with latest scores of 1 or 3
#| fig-pos: H

# Building size and proportion of score 1 in service log

apartment$building_size <- cut(
  apartment[["CONFIRMED UNITS"]],
  breaks = size_breaks,
  labels = size_labels)

service <- apartment |>
  filter(`TENANT SERVICE REQUEST LOG` %in% c(1, 3)) |>
  group_by(building_size) |>
  summarise(buildings = n(), 
            service_percent = mean(`TENANT SERVICE REQUEST LOG` == 1),
            .groups = "drop")

ggplot(service, aes(x = building_size, y = service_percent)) +
  geom_col(fill = "grey", width = 0.7) +
  geom_text(aes(label = scales::percent(service_percent, accuracy = 0.1)),
            vjust = -0.5) +
  scale_y_continuous( labels = scales::label_percent(accuracy = 1),
                      limits = c(0, max(service$service_percent) * 1.25),
                      expand = expansion(mult = c(0, 0))) +
  labs(x = "Building Size", y = "Percentage Receiving Score 1") +
  theme_minimal()
```

@fig-sizecounts presents the counts of all four recorded scores across the 3,587 buildings. A score of 3 was the most common rating in every building-size category. Although buildings with 100 or more units had the highest overall count, only 11 of them received a score of 1, compared with 97 buildings in the smallest size group. These counts support the pattern shown in @fig-sizescore, while also showing the distribution of scores 0 and 2.

```{r}
#| label: fig-sizecounts
#| echo: false
#| eval: true
#| warning: false
#| fig-cap: Counts of all four log scores at the latest evaluation of 3,587 buildings, grouped by size
#| fig-pos: H

stacked_data <- apartment |>
  filter(`TENANT SERVICE REQUEST LOG` %in% 0:3) |>
  mutate(log_score = factor(`TENANT SERVICE REQUEST LOG`, 
                            levels = c(1, 0, 2, 3)))

stacked_data$building_size <- cut(
  stacked_data[["CONFIRMED UNITS"]],
  breaks = size_breaks,
  labels = size_labels)

size_totals <- stacked_data |> count(building_size)

ggplot(stacked_data, aes(x = building_size, fill = log_score)) +
  geom_bar(width = 0.72, position = position_stack(reverse = TRUE)) +
  geom_text(data = size_totals, 
            aes(x = building_size, y = n, label = scales::comma(n)),
            inherit.aes = FALSE, vjust = -0.5) +
  scale_fill_manual(name = "Score: ",
                    values = c("0" = "#BC5085", "1" = "grey", "2" = "#FDE2A7",
                               "3" = "#BDE0FE"), breaks = c("0", "1", "2", "3"),
                    labels = c("0: Undefined", "1: Not Completed / Outdated", 
                               "2: N/A", "3: Completed")) +
  scale_y_continuous(labels = scales::label_comma(), 
                     expand = expansion(mult = c(0, 0.08))) +
  labs(x = "Building Size (Number of Units)", y = "Number of Buildings") +
  theme_minimal() +
  theme(legend.position = "right", legend.title = element_text(size = 9),
        legend.text = element_text(size = 6),
        legend.key.size = grid::unit(0.5, "cm")) +
  guides(fill = guide_legend(nrow = 4, byrow = TRUE))
```

These results show an association between building size and log ratings. They do not imply that building size causes differences in record keeping or that tenants in smaller buildings receive poorer service.

### Follow-up Ratings by Building Size

```{r}
#| include: false

# Use each building's latest evaluation overall, then apply score eligibility

scorechange$building_size <- cut(scorechange[["CONFIRMED UNITS"]],
                                 breaks = size_breaks, labels = size_labels)
score1_change <- scorechange |>
  filter(first_date < latest_date, first_score == 1, latest_score %in% c(1, 3)) |>
  mutate(interval_days = as.numeric(latest_date - first_date))

size_change_summary <- score1_change |>
  group_by(building_size) |>
  summarise(total = n(), stayed_at_1 = sum(latest_score == 1),
            percent_stayed_1 = stayed_at_1 / total,
            median_days = median(interval_days), .groups = "drop")
```

The follow-up analysis starts with 438 buildings that scored 1 at their earliest recorded evaluation, where 36 of them had no later evaluation. Among the remaining 402 buildings, 11 had a score of 0 and 17 had a score of 2 at their latest evaluation. Excluding these 28 buildings leaves 374 eligible buildings. 

Building size is measured at the latest evaluation. Within each size group, the percentage scoring 1 again is calculated among eligible buildings. @tbl-followup in the appendix reports the counts, percentages, and median evaluation intervals.

@fig-scorechange shows that smaller buildings were more likely to receive a score of 1 again. Among buildings with 10–19 units, 23.8% scored 1 at their latest evaluation. The percentage was 16.1% for buildings with 20–49 units, and 14.3% for buildings with 50–99 units. The percentage was lowest among buildings with 100 or more units, at 2.6%. Overall, 307 of the 374 buildings improved from a score of 1 to 3, while 67 received a score of 1 again.

```{r}
#| label: fig-scorechange
#| echo: false
#| eval: true
#| warning: false
#| fig-cap: Percentage scoring 1 again among 374 buildings that initially scored 1 and were later scored 1 or 3, grouped by latest unit count
#| fig-pos: H

ggplot(size_change_summary, aes(x = building_size, y = percent_stayed_1)) +
  geom_col(fill = "grey", width = 0.7) +
  geom_text(aes(label = scales::percent(percent_stayed_1, accuracy = 0.1)),
            vjust = -1, colour = "black") +
  scale_y_continuous(labels = scales::label_percent(), limits = c(0, 0.32),
                     expand = expansion(mult = c(0, 0))) +
  labs(x = "Building Size (Number of Units)",
       y = "Percentage of Scoring 1 Again") +
  theme_minimal()
```

This pattern suggests that improvement in recorded log ratings was more common among larger buildings in the follow-up sample. However, the two largest size categories contain only 35 and 38 buildings, respectively, so their percentages depend on relatively few observations.

### Log Ratings by Ward

Log ratings may vary across wards, partly because wards have different mixes of building sizes. To account for this, each ward’s percentage of buildings scoring 1 is compared with a benchmark that reflects its composition of building sizes. To calculate this benchmark, each building is assigned the citywide score-1 percentage for its size category. These percentages are then averaged across the buildings in the ward. Only buildings with scores of 1 or 3 are included. The calculation is explained step by step in [ward benchmark calculation](#sec-wardbenchmark) in the appendix.

@fig-ward compares the observed and benchmark percentages. A filled point to the right of its benchmark means the ward has a higher percentage of low ratings than the benchmark; a point to the left means a lower percentage. The figure shows only the 21 wards with at least 50 eligible buildings, but buildings from all 25 wards are used to calculate the benchmarks.

Among the displayed wards, Parkdale-High Park had the largest positive difference: 10.8% of eligible buildings scored 1, compared with a benchmark of 6.3%, a difference of 4.5 percentage points. Eglinton-Lawrence also exceeded its benchmark, with an observed percentage of 11.3% compared with 7.5%. In contrast, Etobicoke Centre had the largest negative difference, with 1.6% scoring 1 compared with a benchmark of 5.2%.

These comparisons show that differences in building size do not fully explain why low ratings are more common in some wards than others. Some wards have higher percentages of low ratings than their benchmarks, while others have lower percentages.

```{r}
#| label: fig-ward
#| echo: false
#| eval: true
#| warning: false
#| fig-cap: Filled points show observed score-1 percentages, and open points show benchmarks based on each ward’s building-size mix, using latest scores of 1 or 3
#| fig-pos: H

ward_data <- apartment |>
  filter(`TENANT SERVICE REQUEST LOG` %in% c(1, 3)) |>
  mutate(size_band = cut(`CONFIRMED UNITS`, breaks = size_breaks,
                         labels = size_labels),
         score1 = `TENANT SERVICE REQUEST LOG` == 1)

city_rates <- ward_data |>
  group_by(size_band) |>
  summarise(city_rate = mean(score1), .groups = "drop")

ward_summary <- ward_data |>
  left_join(city_rates, by = "size_band") |>
  group_by(WARDNAME) |>
  summarise(buildings = n(), observed = mean(score1), 
            benchmark = mean(city_rate), .groups = "drop") |>
  filter(buildings >= 50) |>
  mutate(gap = observed - benchmark) |>
  arrange(gap) |>
  mutate(ward_label = paste0(WARDNAME, " (n=", buildings, ")"),
         ward_label = factor(ward_label, levels = ward_label))

ggplot(ward_summary, aes(y = ward_label)) +
  geom_segment(aes(x = benchmark, xend = observed, yend = ward_label),
               color = "grey70", linewidth = 0.9) +
  geom_point(aes(x = benchmark, shape = "Size-mix benchmark",
                 color = "Size-mix benchmark"), size = 3, stroke = 1.2) +
  geom_point(aes(x = observed, shape = "Observed rate", 
                 color = "Observed rate"), size = 2) +
  scale_shape_manual(name = NULL, values = c("Observed rate" = 16, 
                                             "Size-mix benchmark" = 1)) +
  scale_color_manual(name = NULL, values = c("Observed rate" = "#A94C41",
                                             "Size-mix benchmark" = "#4F6874")) +
  scale_x_continuous(labels = scales::label_percent(accuracy = 1),
                     limits = c(0, 0.15), breaks = seq(0, 0.14, 0.02)) +
  labs(x = "Percentage of Buildings Receiving Score 1", y = NULL) +
  theme_minimal() +
  theme(legend.position = "top")
```

# Discussion {#sec-discussion}

## Building Size and Record Keeping

Low tenant-service-log ratings were more common among smaller buildings. The follow-up analysis also showed that, among buildings that initially scored 1, smaller buildings were more likely to score 1 again. However, improvement was common overall, with 307 of the 374 buildings in the follow-up sample improving from a score of 1 to 3.

Differences in management practices may help explain this pattern. A U.S. survey of owners and managers of properties with 5 to 49 units found that owners with larger rental portfolios were more likely to use property-management software and other technology [@manji2024, p. 15]. Such tools could help organize tenant-service records. However, the portfolio size discussed in the survey refers to all units an owner holds, whereas this study measures the size of individual buildings. Management staff and software use were not examined here, and their role in Toronto’s log ratings remains a possible explanation. Future research could examine these practices and whether additional guidance would help buildings maintain complete and up-to-date logs.

## Ward Differences

Some wards had more low log ratings than their mix of building sizes would suggest. For example, Parkdale-High Park and Eglinton-Lawrence had higher percentages of low ratings than their benchmarks. This means that differences in the proportions of small and large buildings do not fully explain the differences between wards.

Other differences between wards, such as household income, housing costs, and the proportion of households that rent, could provide additional context for these patterns. Building ownership and management practices may also be relevant. Wards with percentages above their benchmarks could be starting points for investigating why incomplete or outdated logs are more common in some areas.

## Limitations and Future Work

The tenant-service-log score measures whether records were complete and up to date at the time of evaluation. It does not directly measure how quickly requests were addressed, the quality of repairs, or tenants’ satisfaction. The ratings reflect officers’ assessments rather than tenants’ own opinions. Problems that tenants did not report or that management did not record may therefore be missing from the study.

A study of New York City’s 311 system found differences in complaint behaviour across neighbourhoods after comparing buildings with similar physical conditions [@kontokosta2017]. Toronto’s log ratings assess record keeping rather than complaint counts, but the previously mentioned study tells a related concern: recorded information may not capture all problems tenants experience. This points to a limitation of this study: complete logs do not necessarily include all tenant concerns. Future research could use tenant surveys or interviews, in addition to response times and log ratings, to examine these gaps.

Evaluation timing also affects the comparisons. In the eligible follow-up sample, the median interval between the earliest and latest evaluations was 737 days (@tbl-followup), with individual intervals ranging from 530 to 1,157 days. Evidently, some buildings had more time to improve their logs. Moreover, a score of 1 at both evaluations does not mean the log was incomplete or outdated throughout the entire period. Future comparisons could use similar time intervals between evaluations.

The follow-up results include only buildings that initially scored 1 and later received an eligible score. The City also allows owners to request re-evaluations [@toronto_evaluation_criteria], but the data do not show which evaluations were owner-requested. Therefore, buildings with follow-up evaluations may differ from those without follow-up. For example, some owners may have requested another evaluation after improving their logs. Future research could separate these owner-requested evaluations and compare buildings with and without scheduled follow-up.

Finally, the analysis identifies associations rather than causes. Management resources and other building characteristics may also matter. The ward benchmarks consider only four size groups, which may hide differences between buildings within each group. In addition, ward comparisons should be interpreted as differences in recorded log ratings, not rankings of neighbourhood safety or tenant experience.

\newpage

\appendix

# Appendix {.unnumbered}

### Summary Statistics of Confirmed Units {.unnumbered}

```{r}
#| label: tbl-confirmunits
#| tbl-cap: "Summary statistics of confirmed residential units"
#| message: FALSE
#| echo: FALSE
#| tbl-pos: H

units <- apartment[["CONFIRMED UNITS"]]

# Table: numeric characteristics of the latest-evaluation buildings.

unit_summary <- data.frame(
  Statistic = c("Number of Buildings", "Missing", "Minimum", "Maximum", "Mean", "Median"), 
  "Confirmed Units" = c(
    formatC(sum(!is.na(units)), format = "f", digits = 0, big.mark = ","),
    formatC(sum(is.na(units)), format = "f", digits = 0, big.mark = ","),
    formatC(min(units, na.rm = TRUE), format = "f", digits = 0, big.mark = ","),
    formatC(max(units, na.rm = TRUE), format = "f", digits = 0, big.mark = ","),
    formatC(mean(units, na.rm = TRUE), format = "f", digits = 1, big.mark = ","),
    formatC(median(units, na.rm = TRUE), format = "f", digits = 0, big.mark = ",")),
  check.names = FALSE)

tt(unit_summary) |>
  style_tt(j = 2, align = "r")
```

### Follow-up Sample {.unnumbered}

```{r}
#| label: tbl-followup
#| tbl-cap: "Follow-up counts and intervals by building size"
#| echo: false
#| message: false
#| tbl-pos: H

followup_table <- size_change_summary |>
  transmute(`Size (Units)` = as.character(building_size),
            Eligible = total,
            `Scored 1 Again` = stayed_at_1,
            `Share (%)` = 100 * percent_stayed_1,
            `Median Gap (Days)` = median_days) |>
  bind_rows(tibble(
    `Size (Units)` = "Overall",
    Eligible = nrow(score1_change),
    `Scored 1 Again` = sum(score1_change$latest_score == 1),
    `Share (%)` = 100 * mean(score1_change$latest_score == 1),
    `Median Gap (Days)` = median(score1_change$interval_days)
  ))

tt(followup_table) |>
  format_tt(escape = TRUE) |>
  format_tt(j = c(2, 3, 5), digits = 0, num_fmt = "decimal") |>
  format_tt(j = 4, digits = 1, num_fmt = "decimal") |>
  style_tt(j = 2:5, align = "r")
```

### Calculation of ward benchmarks {#sec-wardbenchmark .unnumbered}

1.  **Select eligible buildings.** Take the latest evaluation for each building and include only buildings with tenant-service-log scores of 1 or 3.

2.  **Assign building-size categories.** Group buildings by their confirmed unit counts: 10–19, 20–49, 50–99, and 100+ units.

3.  **Calculate citywide percentages.** Within each size category, divide the number of buildings scoring 1 by the number scoring either 1 or 3. The resulting percentages are approximately 13.8%, 8.1%, 3.1%, and 1.0%, respectively.

4.  **Calculate each ward’s size proportions.** Within a ward, count the eligible buildings in each size category. Divide each count by the ward’s total number of eligible buildings. These four proportions are the weights.

5.  **Calculate the benchmark.** Multiply each citywide percentage from Step 3 by the corresponding ward weight from Step 4. Add the four results. A size category containing no eligible buildings in a ward receives a weight of zero.

For example: Parkdale-High Park contains 195 eligible buildings: 37 with 10–19 units, 64 with 20–49 units, 49 with 50–99 units, and 45 with 100 or more units. Its benchmark is calculated as:

$$
\frac{37}{195}\times 0.138
+\frac{64}{195}\times 0.081
+\frac{49}{195}\times 0.031
+\frac{45}{195}\times 0.010
\approx 6.29 \%.
$$

\newpage

# References
